External validation

### 2020-09-03 diagnostics/README.Rmd
försöker med README.md

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_folding: show
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
---

@@

Install and attatch some useful packages

@@

Load the exported models to validate (the R object previously sent, probably with another path). This is a nested data frame with one row for each prediction period (90 days and 2 years). Column `fit` contains `glm` object stripped from any personal patient data.

@@

```{r}
names(ext_val_required_data)
```
Some of those are factor variables:
```{r}
ext_val_required_data %>% 
  select(is.factor) %>% 
  pivot_longer(everything(), values_ptypes = list(value = character())) %>% 
  distinct() %>% 
  arrange(name, value) %>% 
  group_by(name) %>% 
  mutate(name = replace(name, duplicated(name), ""))
```
- `P_Sex` and `P_ASA` should be self-explanatory
- `P_BMI` is a broader categorization based on BMI and the [WHO classification] (https://www.euro.who.int/en/health-topics/disease-prevention/nutrition/a-healthy-lifestyle/body-mass-index-bmi) where overweight = "pre-obesity"  
- `P_DiaGrp` is based on ICD-10 codes recorded in SHAR and grouped into broader categories as found in a separate CSV-file:

>>>>

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: show
    keep_md: yes
  md_document:
    variant: markdown_github
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
---

@@

Install and attach some useful packages

@@

Load the exported models to validate (also found "manually" at [Github](https://github.com/eribul/NH_luxation_infektion/blob/master/cache/ext_val_required_data.RData)). This is a nested data frame with one row for each prediction period (90 days and 2 years). Column `fit` contains `glm` objects stripped from any personal patient data.

@@

```{r}
names(ext_val_required_data)
```
Some of those are factor variables:
```{r}
ext_val_required_data %>% 
  select(where(is.factor)) %>% 
  pivot_longer(everything(), values_ptypes = list(value = character())) %>% 
  distinct() %>% 
  arrange(name, value) %>% 
  group_by(name) %>% 
  mutate(name = replace(name, duplicated(name), ""))
```
- `P_Sex` and `P_ASA` should be self-explanatory
- `P_BMI` is a broader categorization based on BMI and the [WHO classification] (https://www.euro.who.int/en/health-topics/disease-prevention/nutrition/a-healthy-lifestyle/body-mass-index-bmi) where overweight = "pre-obesity"  
- `P_DiaGrp` is based on ICD-10 codes recorded in SHAR and grouped into broader categories as found in a separate CSV-file:
